*Prochlorococcus marinus* responses to light and oxygen

### 2024-02-16 Code/Manuscript_O2.Rmd
Fixed some fig captions Fixed Aurora's text that was boxed in a different text box

MED4PAR_cap <- glue("**Chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* MED4 (High Light (HLI) near surface clade) vs. photoperiod (h).  **",

@@

SS120PAR_cap <- glue("**Chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* SS120 (Low Light (LLIII) deep ocean clade) vs. photoperiod (h). **",

@@

MIT9313PAR_cap <- glue("**Chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 (Low Light (LLIV) deep ocean clade) vs. photoperiod (h). **",

@@

MED4GAM_cap <- glue("**A contour plot of a Generalized Additive Model (GAM) representing the chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* MED4 grown under 660 nm (red) and 450 nm (blue) light.**",
                    "The x-axis is photoperiod (h).",
                    "The y-axis is actinic Photosynethetic Active Radiation (PAR) level (µmol photons m^-2^ s^-1^).",
                    "**A.** represents the model under 250 µM of O~2~ and red light.",
                    "**B.** represents the model under 25 µM of O~2~ and red light.",
                    "**C.** represents the model under 250 µM of O~2~ and blue light.",
                    "**D.** represents the model under 25 µM of O~2~ and blue light.",
                    "The legend represents a colour gradient of growth rate from no growth (white) to 1 d^-1^ (dark blue).",
                    "The labeled contour lines indicate the 90%, 50%, and 10% quantiles for achieved growth rate.",

@@

SS120GAM_cap <- glue("**A contour plot of a Generalized Additive Model (GAM) representing the chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* SS120 grown under 660 nm (red) and 450 nm (blue) light.**",
                    "The x-axis is photoperiod (h).",
                    "The y-axis is actinic Photosynethetic Active Radiation (PAR) level (µmol photons m^-2^ s^-1^).",
                    "**A.** represents the model under 250 µM of O~2~ and red light.",
                    "**B.** represents the model under 25 µM of O~2~ and red light.",
                    "**C.** represents the model under 250 µM of O~2~ and blue light.",
                    "**D.** represents the model under 25 µM of O~2~ and blue light.",
                    "The legend represents a colour gradient of growth rate from no growth (white) to 1 d^-1^ (dark blue).",
                    "The labeled contour lines indicate the 90%, 50%, and 10% quantiles for achieved growth rate.",

@@

MIT9313GAM_cap <- glue("**A contour plot of a Generalized Additive Model (GAM) representing the chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 grown under 660 nm (red) and 450 nm (blue) light.**",
                    "The x-axis is photoperiod (h).",
                    "The y-axis is actinic Photosynthetically Active Radiation (PAR) level (µmol photons m^-2^ s^-1^).",
                    "**A.** represents the model under 250 µM of O~2~ and red light.",
                    "**B.** represents the model under 25 µM of O~2~ and red light.",
                    "**C.** represents the model under 2.5 µM of O~2~ and red light.",
                    "**D.** represents the model under 250 µM of O~2~ and blue light.",
                    "**E.** represents the model under 25 µM of O~2~ and blue light.",
                    "**F.** represents the model under 2.5 µM of O~2~ and blue light.",
                    "The legend represents a colour gradient of growth rate from no growth (white) to 1 d^-1^ (dark blue).",
                    "The labeled contour lines indicate the 90%, 50%, and 10% quantiles for achieved growth rate.",

@@

AllStrainPurFitsPlots_cap <- glue("**Chlorophyll specific growth rate (d^-1^) vs. cumulative diel Photosynthetic Usable Radiation (PUR, µmol photons m^-2^ d^-1^).**",
                    "**A.** MED4 High Light I ecotype under 250, 25, or 2.5 µM of O~2~.",
                    "**B.** SS120 Low Light II/III (LLII/III) ecotype under 250, 25, or 2.5 µM of O~2~.",
                    "**C.** MIT9313 Low Light IV (LLIV) ecotype under 250, 25, or 2.5 µM of O~2~.",
                    "3 levels of imposed dissolved O~2~ concentrations (µM) are in rows for each strain.",
                    "Shapes show the imposed photoperiod (h); 4 h (hollow inverted triangle),  8 h (solid diamond), 12 h (solid circle), 16 h (solid upright triangle).",
                      "Symbol colours show the spectral waveband for growth; white LED (black symbols), 660 nm (red symbols), and 450 nm (blue symbols).",
                      "Large symbols show mean of growth rate from logistic curve fits; small symbols show values for replicate determinations, if any.",
                    "Platt (add Platt citation here) 4 parameter model fits to data pooled for each combination of strain and dissolved oxygen shown with solid lines. Seperate models fit to photoperiod data and shown if significantly different from the pooled model; 4 h (long dashed line); 8 h (dotted line); 12 h (dashed line); and 16 h (dot dashed line). ",
                       .sep = " ")

>>>>

MED4PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MED4 (High Light (HLI) near surface clade) vs. photoperiod (h).  **",

@@

SS120PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* SS120 (Low Light (LLIII) deep ocean clade) vs. photoperiod (h). **",

@@

MIT9313PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 (Low Light (LLIV) deep ocean clade) vs. photoperiod (h). **",

@@

MED4GAM_cap <- glue("**A contour plot of a Generalized Additive Model (GAM) representing the chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MED4 grown under 660 nm (red) and 450 nm (blue) light.**",
                    "X-axis is photoperiod (h).",
                    "Y-axis is actinic Photosynethetic Active Radiation (PAR, µmol photons m^-2^ s^-1^).",
                    "**A.** represents the model under 250 µM of O~2~ and red light.",
                    "**B.** represents the model under 25 µM of O~2~ and red light.",
                    "**C.** represents the model under 250 µM of O~2~ and blue light.",
                    "**D.** represents the model under 25 µM of O~2~ and blue light.",
                    "Legends represent a colour gradient of growth rate from no growth (white) to 1.00 d^-1^ (dark red or dark blue).",
                    "Labeled contour lines indicate the 90%, 50%, and 10% quantiles for achieved growth rate.",

@@

SS120GAM_cap <- glue("**Contour plot of a Generalized Additive Model (GAM) representing the chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* SS120 grown under 660 nm (red) and 450 nm (blue) light.**",
                    "X-axis is photoperiod (h).",
                    "Y-axis is actinic Photosynethetic Active Radiation (PAR, µmol photons m^-2^ s^-1^).",
                    "**A.** represents the model under 250 µM of O~2~ and red light.",
                    "**B.** represents the model under 25 µM of O~2~ and red light.",
                    "**C.** represents the model under 250 µM of O~2~ and blue light.",
                    "**D.** represents the model under 25 µM of O~2~ and blue light.",
                    "Legends represent a colour gradient of growth rate from no growth (white) to 1.00 d^-1^ (dark red or dark blue).",
                    "Labeled contour lines indicate the 90%, 50%, and 10% quantiles for achieved growth rate.",

@@

MIT9313GAM_cap <- glue("**Contour plot of a Generalized Additive Model (GAM) representing the chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 grown under 660 nm (red) and 450 nm (blue) light.**",
                    "X-axis is photoperiod (h).",
                    "Y-axis is actinic Photosynthetically Active Radiation (PAR, µmol photons m^-2^ s^-1^).",
                    "**A.** represents the model under 250 µM of O~2~ and red light.",
                    "**B.** represents the model under 25 µM of O~2~ and red light.",
                    "**C.** represents the model under 2.5 µM of O~2~ and red light.",
                    "**D.** represents the model under 250 µM of O~2~ and blue light.",
                    "**E.** represents the model under 25 µM of O~2~ and blue light.",
                    "**F.** represents the model under 2.5 µM of O~2~ and blue light.",
                    "Legends represent a colour gradient of growth rate from no growth (white) to 1.00 d^-1^ (dark red or dark blue).",
                    "Labeled contour lines indicate the 90%, 50%, and 10% quantiles for achieved growth rate.",

@@

AllStrainPurFitsPlots_cap <- glue("**Chlorophyll specific growth rate (d^-1^) vs. cumulative diel Photosynthetic Usable Radiation (PUR, µmol photons m^-2^ d^-1^).**",
                    "**A.** MED4 High Light I ecotype under 250, 25, or 2.5 µM of O~2~.",
                    "**B.** SS120 Low Light II/III (LLII/III) ecotype under 250, 25, or 2.5 µM of O~2~.",
                    "**C.** MIT9313 Low Light IV (LLIV) ecotype under 250, 25, or 2.5 µM of O~2~.",
                    "3 levels of imposed dissolved O~2~ concentrations (µM) are in rows for each strain.",
                    "Shapes show the imposed photoperiod (h); 4 h (hollow inverted triangle),  8 h (solid diamond), 12 h (solid circle), 16 h (solid upright triangle).",
                      "Symbol colours show the spectral waveband for growth; white LED (black symbols), 660 nm (red symbols), and 450 nm (blue symbols).",
                      "Large symbols show mean of growth rate from logistic curve fits; small symbols show values for replicate determinations, if any.",
                    "Platt (add Platt citation here) 4 parameter model fit to data pooled for each combination of strain and dissolved oxygen shown with solid lines. Seperate models fit to photoperiod data and shown if significantly different from the pooled model; 4 h (long dashed line); 8 h (dotted line); 12 h (dashed line); and 16 h (dot dashed line). ",
                       .sep = " ")
